### 2016-11-12 thesis/intro/intro.tex
tmp commit

The first mutation that should be mentioned is in the leptin gene.
\\

LEP, LEPR, POMC, CART, MC4R, etc and its associated genetic/biological mechanisms\\

\citep{Montague1997}
\citep{Clement1998}
\citep{Jackson1997}
\citep{Krude1998}
\citep{Farooqi2003}
\citep{Kublaoui2006}
\citep{Dubern2001}
\citep{Challis2002}

>>>>

The first mutation that should be mentioned is in the leptin gene.
\citet{Montague1997} found a single nucleotide deletion mutation at position 133 of the leptin gene in children with early-onset obesity.
They further showed that the mutation caused a frameshift mutation in the protein, resulting in an inactive form of leptin that was not able to be secreted \citep{Montague1997}.

In close relation to this mutation is the mutation in the leptin receptor gene.
\citet{Clement1998} have discovered a single nucleotide substitution mutation that led to the leptin receptor transcript that skipped exon 16 -- leading to a form of the receptor with no transmembrane or intracellular domain.
Individuals with this rare mutation showed extreme hyperphagia and symptoms of early-onset obesity, even though their circulating leptin levels were present abundantly \citep{Clement1998}.

\citep{Jackson1997}
\citep{Krude1998}
\\

\citep{Farooqi2003}
\citep{Kublaoui2006}
\citep{Dubern2001}
\citep{Challis2002}
\\
